---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Female Power}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css


```{r, echo=FALSE}
## set.seed(121121) # set seed for random number generator to give repeatable results

## ## sample size
## ssizes <- c(500, 750, 1000, 1250, 1500, 1750, 2000, 2250, 2500, 2750, 3000)
## names(ssizes) <- paste0("size_", ssizes)

## ## location effect size: female same (1) up to 2-fold more in prey 
## loc <- seq(1, 1, by=0.1)
## names(loc) <- paste0("loc_", loc)

## ## plain sex effect size: female same (1) up to 2-fold more in prey 
## sex <- seq(1, 1.5, by=0.05)
## names(sex) <- paste0("sex_", sex)

## n.reps <- 100

## sex.p <- mclapply(ssizes, function(s.size){
##     mclapply(sex, function(sexEff){
##         ## effect size: female same (1) up to 2-fold more high density
##         reps <- sapply(1:n.reps, function (i){
##             dat <- simulate.wolfData(s.size, effMF=sexEff, effDens=1)
##             mod <- lme4::glmer(response ~ prey.sex + location.wolf.density +
##                                    (1 | location) + (1 | wolf), 
##                                family = 'poisson', data = dat)
##             sW <- summary(mod)
##             sW$coefficients[2, "Pr(>|z|)"] > 0.05
##         })
##         sum(reps)/n.reps
##     }, mc.cores=3)
## }, mc.cores=7)


## loc.p <- mclapply(ssizes, function(s.size){
##     mclapply(loc, function(locEff){
##         reps <- sapply(1:n.reps, function (i){
##             dat <- simulate.wolfData(s.size, 1, locEff)
##             mod <- lme4::glmer(response ~ prey.sex + location.wolf.density +
##                                    (1 | location) + (1 | wolf), 
##                                family = 'poisson', data = dat)
##             sW <- summary(mod)
##             sW$coefficients[3, "Pr(>|z|)"]>0.05
##         })
##         sum(reps)/n.reps
##     }, mc.cores=3)
## }, mc.cores=7)


## ## Sex
## powerS <- melt(sex.p)

## names(powerS) <- c("power", "effSizeSex", "sampleSize")

## powerS$effSizeSex <- as.numeric(gsub("sex_", "", powerS$effSizeSex))

## powerS$effSizeSex <- factor(paste0((powerS$effSizeSex), "*"),
##                             levels=unique(paste0((powerS$effSizeSex), "*")))

## powerS$sampleSize <- as.factor(as.numeric(gsub("size_" ,"", powerS$sampleSize)))

## powerS  <- spread(powerS, effSizeSex, power)

## rownames(powerS) <- powerS$sampleSize

## powerS$sampleSize <- NULL

## sexPheat <- pheatmap(powerS, cluster_rows=FALSE, cluster_cols=FALSE,
##                      main = paste("Proportion of false negative findings for\n",
##                                   "deviations in prey sex from 50%"))

## pdf("Sex_power.pdf", width=5, height=5)
## grid.arrange(grobs = list(sexPheat[[4]]),
##              ## list(sexPheat[[4]][-3,]) for removing legend?
##              right = textGrob("Sample size",  rot=270),
##              bottom = textGrob(paste0("Rate ratio for female over male prey\n", 
##                                       "(fold increase of female over male)")))
## dev.off()



## ## Location
## powerL <- melt(loc.p)

## names(powerL) <- c("power", "effSizeLoc", "sampleSize")

## powerL$effSizeLoc <- as.numeric(gsub("loc_", "", powerL$effSizeLoc))

## powerL$effSizeLoc <- factor(paste0((powerL$effSizeLoc), "*"),
##                             levels=unique(paste0((powerL$effSizeLoc), "*")))

## powerL$sampleSize <- as.factor(as.numeric(gsub("size_" ,"", powerL$sampleSize)))

## powerL  <- spread(powerL, effSizeLoc, power)

```


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
